A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-15 6_validation.tex
move accuracy figure down
fix reference for linear advance

\subsection{Experimentation}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance~\cite{linadvance}: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.
We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

>>>>

\subsection{Experimentation}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance~\cite{tronvoll2019investigating}: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.
We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
